---
title: "Technical"
author: "Madeline Gorchels"
date: "5/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
```

```{r}
survey = read_csv("HW3Data.csv") 

#converting risk to decimal
survey_2 <- survey %>% 
  transform(risk_dec = risk/100)

```

1. Create a linear probability model that predicts a respondent’s probability of voting ‘yes’ on the
ballot based on their age, income, NEP score, the risk reduction offered by the program, and the
cost of the program to that respondent. Show the model and interpret the regression
coefficients.

```{r}
survey_mod = lm(vote~risk_dec+bid+age+NEP+income, data = survey_2)

summary(survey_mod)
```
```{r}

```


2. Based on this regression, what can you say about the value of a single prevented whale death?
(Hint: Think about how risk reduction for all whales translates into the number of whale deaths
avoided)




3. Pick three arbitrary respondents. For each of those respondents, estimate their WTP for a VSR
program offering 60% risk reduction.



4. Now repeat this process and estimate the mean WTP for a VSR program offering 60% risk
reduction among Santa Barbara County households.


5. If there are 150,000 households in Santa Barbara County, estimate the total benefit of a VSR
program to these households.


6. Based only on these benefits, do the benefits of the VSR program outweigh the costs?


When a container ship reduces its speed, it not only reduces the risk of colliding with a whale but also
emits less carbon per distance traveled. For this reason, the WhaleStrikes Group Project recommended
enrolling container ships in voluntary carbon trading markets to mitigate fatal whale strikes. Assume
that for any ship transiting the Santa Barbara Channel, a speed reduction (that results in a 60% risk
reduction) will cost the shipper $1,000, but will result in 20 fewer tons of CO2 emitted per transit.

7. Suppose the price of a carbon credit is $Z per ton, at what price Z* will the shipping industry
decide to adopt the VSR for purely self-interested reasons? (Note: if ships voluntarily reduce
speed, then the $7 million cost (noted above) of implementing the VSR would be avoided)

8. Now suppose the carbon credit price is exactly Z*, so all ships voluntarily reduce speed to
achieve the 60% risk reduction. Approximately how many whales would be saved by this? What
would be the social value of allowing ships to enter the carbon trading market?
